\documentclass[12pt]{article} 
\usepackage{url}
\usepackage{hyperref}

\usepackage{calc,url}

\usepackage{epsfig,amsmath}

\newcommand{\reals}{\mathbf{R}}

\usepackage[short,us]{datetime}
\newdateformat{mydate}{\THEMONTH \, / \THEDAY}

\mydate


\newcounter{hw}\setcounter{hw}{0}
\newcommand{\hw}{%\
\setcounter{hw}{\value{hw}+1}
\thehw \,\,}

\newcounter{qz}\setcounter{qz}{0}
\newcommand{\qz}{%\
\setcounter{qz}{\value{qz}+1}
\theqz \,\,}

\newcounter{ex}\setcounter{ex}{0}
\newcommand{\ex}{%\
\setcounter{ex}{\value{ex}+1}
\theex}



\newcounter{wk}\setcounter{wk}{0}
\newcommand{\wk}{%\
\setcounter{wk}{\value{wk}+1}
\thewk \,\,}

\newcounter{dy}\setcounter{dy}{0}
\newcommand{\dy}{%\
\setcounter{dy}{\value{dy}+1}
\thedy \,\,}

% cd = class day
\newcounter{cd}\setcounter{cd}{24}
\newcommand{\cd}{%\
\setcounter{cd}{\value{cd}+1}
\thecd \,\,}

\newcounter{cmon}\setcounter{cmon}{8}
\newcommand{\cmon}{%\
\setcounter{cmon}{\value{cmon}+1}
\thecmon \,\,}

\newcounter{cy}\setcounter{cy}{\the\year}
\newcommand{\cy}{%\
\setcounter{cy}{\value{cy}+1}
\thecy \,\,}


\frenchspacing
\usepackage[margin=0.5in]{geometry}
\usepackage[activate={true,nocompatibility},final,tracking=true,kerning=true,spacing=true,factor=1100,stretch=10,shrink=10]{microtype}

\usepackage[american]{babel}
\usepackage[T1]{fontenc}
\usepackage{fourier}

\newcommand{\term}{Fall}
\newcommand{\course}{MATH 115--02,  Calculus I with Analytic Geometry}
\begin{document}

\subsubsection*{FAQ}


\begin{enumerate}

\item \textbf{Question} Did I miss anything in class last week?

\textbf{Answer} Yes.  Please read  the poem “Did I Miss Anything?” by Tom Wayman.  

%\item  \textbf{Question}  Will  we review the entire dead week?

%\textbf{Answer} Maybe.  Once we finish \S1.1 -- \S6.3, we'll review for the remainder of the term.  But it's likely that we'll need to use at least part of dead week to catch up. 


\item  \textbf{Question}  Will you give us a review before every exam?

\textbf{Answer} Yes. The review will likely not have a complete solution key, but yes there will be a review. The review for the final exam will be the union of all the other reviews.  We might spend some class time before an exam for review, but it's unlikely we'll spend the entire class period reviewing. 

\item  \textbf{Question}  Can I get extra credit?

\textbf{Answer} No. Our syllabus gives our grading scale and assessments. Course grades for all students will be
assigned according to the syllabus.

\item  \textbf{Question}  Will you sign my grade check form?

\textbf{Answer} Yes.  Please help me out and look up your course grade on Canvas and show it to me.

\item  \textbf{Question}  My major is X and I have to take Calculus II.  I've heard that Calculus II is much harder than Calculus I.  Should I switch majors?

\item  \textbf{Answer}  No, not for that reason. Calculus II is no more intellectually challenging than Calculus I. All science majors have required classes (for example, Physical Chemistry, Quantum Mechanics, etc) that
are \emph{far} more difficult than Calculus II. 

\item  \textbf{Question} Isn't \(1/0\) \emph{really} equal to infinity?

\item  \textbf{Answer}  No,  the rule  \(1/0 = \infty\)  is rubbish. If we adopted    \(1/0 = \infty\) as a rule and kept the other usual rules of arithmetic, we'd be able to derive statements that
are manifestly false (things like \(1 = 2\)).


\item  \textbf{Question} Isn't \(1/\infty \) \emph{really} equal to zero?

\item  \textbf{Answer}  No,  \(1/\infty = 0\)  is rubbish.  The reason is much the same as for why  \(1/0 = \infty\)  is rubbish.  Possibly the confusion stems from the limit fact that if \(\displaystyle \lim_{x \to a} F(x) = 1\) and  \(\displaystyle  \lim_{x \to a} G(x) =  \infty\), we have \(\displaystyle \lim_{x \to a} \frac{F(x)}{G(x)} = 0\).  Arguably, the calculation \(\displaystyle \lim_{x \to a} \frac{F(x)}{G(x)} =\frac{1}{\infty} = 0\) is a forgivable faux pas, but this limit fact  doesn't imply that  \(1/\infty = 0\).


\item  \textbf{Question} Is \(0^0\) undefined?

\item  \textbf{Answer} Sometimes, but not always.  In the context of a summation, such as \(\sum_{k=0}^{n} x^k\),  the first term is \(x^0\). If \(0^0\) is undefined, the first term of the sum is
undefined when \(x=0\). But in the context of a sum of powers of a variable, we almost always want \(x^0 = 1\) for all \(x\).  In other contexts,  \(0^0\) is undefined. Mathematical notation, like all natural languages, is context dependent.

\item  \textbf{Question} What is  \(\infty - \infty\)?

\item  \textbf{Answer} It is rubbish.


\item  \textbf{Question}  Is infinity a number?

\item  \textbf{Answer} Yes, infinity is a number.  It's not a \emph{real} number, but it is a number.

\item  \textbf{Question}  Can a function be infinity?

\item  \textbf{Answer} No. Functions and numbers are distinct objects, so a function can \emph{never} be a number. It is possible for infinity to be in the range of a function, for example, \(x \in \reals \mapsto \begin{cases}  x & \mbox{ if } x \neq 2 \\ \infty &  \mbox{ if } x = 2 \end{cases} \).  Although infinity is in the range of this function, the function certainly isn't infinity. Failing to distinguish a function from a number is an example of \emph{conflating}.



\item  \textbf{Question} Why is \(0! = 1\)?

\item  \textbf{Answer} Because it's useful and it extends the validity of a useful identity. For positive integers \(n\) greater than two, we have the identity \(n! = n (n-1)!\). If we replace \(n\) by one in this identity, we get \(0! = 1\). 

\item  \textbf{Question} I saw a proof that \(0=1\).  Is it correct?

\item  \textbf{Answer}  No, it is rubbish. Most likely the so-called proof involved a hidden divide by zero.


\item  \textbf{Question} My cousin told me about a strategy for playing Keno that is guaranteed to win. Does it work?

\item  \textbf{Answer} No. Many such methods involve doubling your bet repeatedly. This scheme is an effective way to convert  a large fortune into a small  fortune.

\item  \textbf{Question}  If a sentence ends with a factorial function, should a period follow the explanation point?

\item  \textbf{Answer}  Yes. But the sentence should be re-written to not end that way.  Writing ``\(x = 0!\).''  is nerd humor for the equivalent statement ``\(x = 1.\)''

\item  \textbf{Question} Does \(\ln x + y\) mean \((\ln x) + y \) or   \(\ln  (x + y)\)?

\item  \textbf{Answer} The standard is that is \(\ln x + y = (\ln x) + y \). But \( \ln x y = \ln(xy)\).  All this is too confusing, so I suggest using parentheses. 

\item  \textbf{Question}  Is it true that \(a \cdot b  + c\) means \(a (b+c)\), but \(a  b  + c\) means \((ab) + c\)?

\item  \textbf{Answer} No.  Both  \(a \cdot b  + c\) and \(a b + c\) mean  \((ab) + c\).  Possibly before about 1940 or so, using a centered dot for multiplication had a lower precedence than for addition. But at least in the United States, this is no longer true.



\item  \textbf{Question}  Is time the fourth dimension?

\item  \textbf{Answer} No, not really.  For many physical theories, it's convenient to lump the three spatial dimensions together with the time, forming a vector with four components. But in mathematics, 
vectors can have any number of components and we don't impose any particular meaning to the components. So I wouldn't say that time is \emph{the} fourth dimension.

\item  \textbf{Question}  Can you see the fourth dimension?

\item  \textbf{Answer} No, absolutely not.

\item  \textbf{Question}  Is mathematics \emph{invented} or \emph{discovered}?

\item  \textbf{Answer} I don't know. It isn't, I think, a question that is worth pondering.

\item  \textbf{Question} Do numbers exist?

\item  \textbf{Answer} I don't know.  Meta-mathematical questions don't interest me all that much. Again, it isn't, I think, a question that is worth pondering.

\item  \textbf{Question} Do the Fibonacci numbers frequently appear in nature?
\item  \textbf{Answer}  No, not really.  For an explanation, read the article ``Fibonacci Flim-Flam,'' by Donald E. Simanek.


\item  \textbf{Question} Are there deep connections between mathematics and music? 

\item  \textbf{Answer}  No, not really. The connections that are known aren't, I would say, particularly deep.


\item  \textbf{Question}  Billy had 53 socks.  Eleven of them were brown.  The rest were navy blue.  He never sorts them, and keeps them all in his drawer.  In the morning, what's the greatest number of socks that he has to pull out before he gets a matching pair?

\item  \textbf{Answer} It depends. Is Billy color blind?  Are the lights on? What does matching mean? Does a wool sock match with a cotton sock? It matters.

\item  \textbf{Question} What's the next number in the sequence  \(2,5,8,11, \dots \)?

\item  \textbf{Answer}  It's a silly problem that deserves a silly answer--any number is just as logical as any other. 
The formula for the sequence might be \(k \in \mathbf{Z}_{\geq 0} \mapsto \begin{cases} 3 k +2 & \mbox{ if } k \leq 3
 \\ \sqrt{2} & \mbox{ if } k >  3 \end{cases} \). That would make the next term \(\sqrt{2} \). Arguably, the formula  \(k \in \mathbf{Z}_{\geq 0}  \mapsto 3 k +2 \) is in some sense the most simple, so by the law of parsimony (the simplest explanation is most likely the right one), the next term is 14.  But this problem doesn't have a unique solution, so the law of parsimony doesn't apply.

\item  \textbf{Question} Is it true that \(1 + 2 + 3 + \cdots = -1/12\)?

\item  \textbf{Answer}  Maybe. For one meaning of the concept of convergence, the answer is yes; for other meanings, including the meaning that you will learn (or learned)  in calculus, the answer is no.  Some physical theories use the notion of convergence for which it is true that \(1 + 2 + 3 + \cdots = -1/12\).

\item  \textbf{Question} Is \(\sqrt{9} = \pm 3\)?

\item  \textbf{Answer}  Maybe.  But for this class, it's best to stick with the so-called principal square root--that means \(\sqrt{9} = 3\), not  \(\sqrt{9} = \pm 3\).

\item  \textbf{Question} Why does my graphing calculator not show the left side of the graph of \(y = x^{2/3}\). 

\item  \textbf{Answer} It's because your calculator is using what is usually known as the principal branch for the \(2/3\) power and not the so-called real-branch rule.  Using the real branch rule,
we have \((-1)^{2/3} = ((-1)^2)^3 = 1^3 = 1\). But using principal branch, we have \((-1)^{2/3} = \frac{\sqrt{3}}{2}  \mathrm{i}  -\frac{1}{2}\) If you would like to understand this, please enroll in MATH 365.

\item  \textbf{Question} Is it true that four current UNK faculty took a math class from you?

\item  \textbf{Answer}  This was  true at one time, but currently I only know of two who took a class from me. I've been told that there is one more, but I don't know who this is.

\item  \textbf{Question} Why did you choose to be a math teacher?


\item  \textbf{Answer} It was a combination of having something close to love for the discipline, growing up in a scientifically based family, and learning from some strong science teachers in high school and college.


\item  \textbf{Question} What is your favorite comfort food?

\item  \textbf{Answer}  For cool weather, it's cornbread (with butter and honey), chili, collard greens, chow-chow, and peach cobbler; for warm weather, it's cold slaw, baked beans, sliced tomatoes, buttered corn on the cob, and peach cobbler.

\item   \textbf{Question}  What is your favorite programming language?

\item  \textbf{Answer}  Common Lisp, definitely. And this is fortunate because I'm a developer for a computer algebra system that is written in Common Lisp. My second favorite language is Julia.

\item   \textbf{Question} Is it true that you hit your head on a TV in class and passed out?

\item   \textbf{Answer} True, but I didn't pass out.

\item   \textbf{Question} Will you tell the story about the time you chased a turkey?

\item   \textbf{Answer}   No, the turkey story has been retired.

\item  \textbf{Question} Has somebody really asked all these questions?

\item  \textbf{Answer}  Except for the next to the last question, yes.
\end{enumerate}

\end{document}
